Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-06-24 manuscript/manuscript.tex
section 3

\subsubsection{Prior Specification}
We adopt a fully Bayesian inferential approach and assign prior distributions to all model parameters. Conveniently, all parameters admit conditionally conjugate priors, which greatly improves posterior computation via a data-augmented Gibbs sampler. For \textbf{[Give priors for each parameter. Be clear about the conditionally joint prior for $\boldsymbol\beta_k$ and $\boldsymbol\Sigma_k$. Where appropriate, explain advantages]}

>>>>

\subsubsection{Prior Specification}
We adopt a fully Bayesian inferential approach and assign prior distributions to all model parameters. Conveniently, all parameters admit conditionally conjugate priors, which greatly improves posterior computation via a data-augmented Gibbs sampler. For the MSN model component, we adopt a conditionally independent prior structure for $\boldsymbol\beta_k$ and $\boldsymbol\Sigma_k$, where $p(\boldsymbol\beta_k,\boldsymbol\Sigma_k) = p(\boldsymbol\Sigma_k)p(\boldsymbol\beta_k|\boldsymbol\Sigma_k)$. We choose the normal-inverse-Wishart distribution for $p(\boldsymbol\beta_k,\boldsymbol\Sigma_k)$ by specifying $\boldsymbol\Sigma_k \sim \text{IW}(\mathbf{V}_k,\nu_k)$ and $\boldsymbol\beta_k|\boldsymbol\Sigma_k \sim \text{N}_{Jp}(\mathbf{b}_k,\mathbf{I}_p \otimes \boldsymbol\Sigma_k)$. For the multinomial logit model component, the regression parameters $\boldsymbol\delta_k$ are given a conjugate $\text{N}_r(\mathbf{d}_k, \mathbf{S}_k)$ prior for $k = 1,...,K-1$.

We allow the normal-inverse-Wishart and multinomial hyperparameters to vary across clusters, though they may be shared across clusters in practice. An advantage of allowing for cluster-specific prior parameters is that \textit{a priori} knowledge of development trends can be incorporated into certain clusters while still allowing the parameters of other clusters to be almost entirely determined by the data. Additionally, prior information regarding the effect of certain covariates on development cluster membership can be incorporated in to the model by choosing informative values for $\mathbf{d}_k \ \text{and} \ \mathbf{S}_k$

\textbf{[Give priors for each parameter. Be clear about the conditionally joint prior for $\boldsymbol\beta_k$ and $\boldsymbol\Sigma_k$. Where appropriate, explain advantages]}
